\documentclass[letterpaper,11pt,oneside]{article}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{xcolor}


\definecolor{brightcerulean}{rgb}{0.11, 0.67, 0.84}
\definecolor{cerulean}{rgb}{0.0, 0.48, 0.65}
\definecolor{denim}{rgb}{0.08, 0.38, 0.74}


\hypersetup{
    colorlinks=true,
    linkcolor=denim,
    filecolor=denim,      
    urlcolor=denim,
    }

\usepackage{longtable}

\usepackage{graphicx} 
\usepackage[left=2cm, right=2cm, bottom=2cm, top=2.5cm]{geometry}
%\usepackage[left=1in, right=1in, bottom=1in, top=1in]{geometry}

% \pagenumbering{arabic}

\usepackage{fancyhdr}
\pagestyle{fancy}
% \renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
% \lfoot{D. Murray-Stoker}
% \rfoot{CV \thepage}
\cfoot{}

\lhead{David Murray-Stoker\hspace{3 mm}---\hspace{3 mm}CV \thepage}
% \rhead{CV \thepage}
\chead{}
% \pagenumbering{gobble} 

\renewcommand\tabcolsep{0.2cm}

\usepackage[none]{hyphenat}
\usepackage{array}
\usepackage{enumitem}
\usepackage{hanging}

\newcommand\hangbibentry[1]{%
    \smallskip\par\hangpara{1em}{1}\bibentry{#1}\smallskip\par 
}

%\newenvironment{absolutelynopagebreak}
%  {\par\nobreak\vfil\penalty0\vfilneg
%   \vtop\bgroup}
 % {\par\xdef\tpd{\the\prevdepth}\egroup
 %  \prevdepth=\tpd}

%%% End preamble %%%





\begin{document}


\thispagestyle{empty}
%%% Personal Information %%%

\noindent  \LARGE{\textbf{David Murray-Stoker}} 
\smallskip
\normalsize

\noindent \begin{tabular}{@{} p{10cm} >{\raggedleft\arraybackslash}p{8.11cm}}
Assistant Professor of Biology & \\

Clayton State University & \\
{\href{mailto:DavidMurray-Stoker@clayton.edu}{DavidMurray-Stoker@clayton.edu}} & \\
{\href{https://dmurraystoker.github.io}{dmurraystoker.github.io}} & \\
{\href{https://scholar.google.com/citations?user=AJuYahkAAAAJ&hl=en}{Google Scholar}} & \\


\end{tabular}
\vspace{1em}

\noindent\hrulefill 

\bigskip





%%% Research Interests %%%

\noindent \begin{tabular}{@{} p{3cm} >{\raggedright}p{14.2cm}}
% \noindent \begin{tabular}{@{} p{3cm} p{14.2cm}}
\Large{\textbf{Research Interests}} & (Meta)community Ecology | Evolutionary Ecology | Urbanization | Species Interactions | STEM Pedagogy | Statistics \& Data Science Education\\
\end{tabular}

\bigskip





%%% Academic Positions %%%

\noindent \begin{tabular}{@{} p{3cm} p{12cm} >{\raggedleft\arraybackslash}p{1.7cm}}
\Large{\textbf{Positions}}    & \textbf{Assistant Professor of Biology} & 2024--Present \\
& School of Sciences & \\
& Clayton State University & \\
\end{tabular}

\bigskip




  
%%% Education %%%

\noindent \begin{tabular}{@{} p{3cm} p{12cm} >{\raggedleft\arraybackslash}p{1.7cm}}
\Large{\textbf{Education}}    & \textbf{University of Toronto} & 2018--2024 \\
& Ph.D. in Ecology \& Evolutionary Biology & \\

& & \\

& \textbf{University of Georgia} & 2011--2016 \\
& B.S. in Ecology \textit{cum laude} & \\

& & \\

& \textbf{University of North Georgia, Gainesville Campus} &  2010--2011 \\
& Formerly Gainesville State College \\
& Prerequisites while dual-enrolled in high school and community college & \\
\end{tabular}

\bigskip





%%% Publications %%%

\noindent\Large{\textbf{Publications} } 
\normalsize
\bigskip

\def\arraystretch{1.4}
\noindent
\begin{longtable}{@{} p{0.5cm} >{\raggedright\arraybackslash}p{16.7cm}}
14. & \hangindent=5mm\textbf{D. Murray-Stoker}, J. S. Santangelo, M. Szulkin, and M. T. J. Johnson. Comparing approaches to quantify urbanization on a multicontinental scale. \textit{bioRxiv} preprint. DOI: \href{https://www.biorxiv.org/content/10.1101/2024.04.30.591983v1}{10.1101/2024.04.30.591983} | \href{https://doi.org/10.5281/zenodo.11038230}{Data \& Code}. \\
13. & \hangindent=5mm\textbf{D. Murray-Stoker},  L. Rossi, and M. T. J. Johnson. Diversity and assembly of the microbiome of a leguminous plant along an urbanization gradient. \textit{bioRxiv} preprint. DOI: \href{https://www.biorxiv.org/content/10.1101/2024.06.10.598260v1}{10.1101/2024.06.10.598260} | \href{https://zenodo.org/records/11550119}{Data \& Code} | \href{https://www.ncbi.nlm.nih.gov/bioproject/PRJNA1107685}{NCBI BioProject} | In revision at \textit{Urban Ecosystems}.\\
12. & \hangindent=5mm\textbf{D. Murray-Stoker},  and M. T. J. Johnson. 2024. Mosaic of local adaptation between white clover and rhizobia along an urbanization gradient. \textit{Journal of Ecology} 112: 1150-1163. DOI: \href{https://onlinelibrary.wiley.com/doi/abs/10.1111/1365-2745.14292}{10.1111/1365-2745.14292} | \href{https://doi.org/10.5281/zenodo.8253951}{Data \& Code} | \href{https://www.ncbi.nlm.nih.gov/bioproject/PRJNA1005557}{NCBI BioProject}. \\
11. & \hangindent=5mmMurray-Stoker, K., J. V. McHugh, A. C. Benke, K. A. Parsons, \textbf{D. Murray-Stoker}, A. D. Rosemond, S. J. Wenger, and D. P. Batzer. 2023. Long-term comparison of invertebrate communities in a blackwater river reveals taxon-specific biomass change. \textit{Freshwater Biology} 68: 632-644. DOI: {\href{https://onlinelibrary.wiley.com/doi/abs/10.1111/fwb.14052}{10.1111/fwb.14052}} | {\href{https://zenodo.org/record/7455905#.Y8F1BezMIbk}{Data \& Code}}\\
10. & \hangindent=5mm\textbf{D. Murray-Stoker}, K. M. Murray-Stoker, F. P. Kong$^{*}$, and F. Amanat$^{*}$. 2022. Environmental filtering and habitat (mis)matching of riverine invertebrate metacommunities. \textit{Journal of Biogeography} 12: 2105-2119. DOI: {\href{http://onlinelibrary.wiley.com/doi/abs/10.1111/jbi.14501}{10.1111/jbi.14501}} | {\href{https://zenodo.org/record/6800554#.Ys9CNOzML0o}{Data \& Code}} | Selected as Editor's Choice \\
9. & \hangindent=5mmMiles, L. S.$^{+}$, \textbf{D. Murray-Stoker}$^{+}$, V. J. Nhan, and M. T. J. Johnson. 2022. Effects of urbanization on specialist herbivorous insect communities of milkweed are mediated by spatial and temporal variation. \textit{Ecosphere} 13: e4222. DOI: {\href{http://onlinelibrary.wiley.com/doi/abs/10.1002/ecs2.4222}{10.1002/ecs2.4222}} | {\href{https://zenodo.org/record/6474064#.Ys9CEezML0o}{Data \& Code}} \\
8. & \hangindent=5mmBarnum, T., R., J. T. Wootton, R. J. Bixby, J. M. Drake, \textbf{D. Murray-Stoker}, C. Colon-Gaud, A. T. Rugenski, T. C. Frauendorf, S. Connelly, S. S. Kilham, M. R. Whiles, K. R. Lips, and C. M. Pringle. 2022. Mechanisms underlying lack of functional compensation by insect grazers after tadpole declines in a Neotropical stream. \textit{Limnology \& Oceanography} 67: S198-S210. DOI: {\href{https://aslopubs.onlinelibrary.wiley.com/doi/full/10.1002/lno.11904}{10.1002/lno.11904}} \\
7. & \hangindent=5mm\textbf{Murray-Stoker, D.}, and M. T. J. Johnson. 2021. Ecological consequences of urbanization on a legume-rhizobia mutualism. \textit{Oikos} 130: 1750-1761. DOI: {\href{https://onlinelibrary.wiley.com/doi/full/10.1111/oik.08341}{10.1111/oik.08341}} | {\href{https://zenodo.org/record/4459724#.YmVqvfPMIbl}{Data \& Code}} \\
6. & \hangindent=5mm\textbf{Murray-Stoker, D}. 2021. On the efficacy of restoration in stream networks: comments, critiques, and prospective recommendations. \textit{Peer Community Journal} 1: e52. DOI: {\href{https://peercommunityjournal.org/articles/10.24072/pcjournal.52/}{10.24072/pcjournal.52}} | {\href{https://doi.org/10.6084/m9.figshare.6448010.v7}{Data \& Code}} \\
5. & \hangindent=5mm\textbf{Murray-Stoker, D.}, and K. M. Murray-Stoker. 2020. Consistent metacommunity structure despite inconsistent drivers of assembly at the continental scale. \textit{Journal of Animal Ecology} 89: 1678-1689. DOI: {\href{http://besjournals.onlinelibrary.wiley.com/doi/abs/10.1111/1365-2656.13220}{10.1111/1365-2656.13220}} | {\href{https://osf.io/62je8/}{Data \& Code}} \\
4. & \hangindent=5mmSantangelo J. S., L. S. Miles, S. T. Breitbart, \textbf{D. Murray-Stoker}, L. R. Rivkin, M. T. J. Johnson, and R. W. Ness. 2020. Urban environments as a framework to study parallel evolution. In: \textit{Urban Evolutionary Biology}. Edited by Marta Szulkin, Jason Munshi-South and Anne Charmantier: Oxford University Press. DOI: {\href{https://oxford.universitypressscholarship.com/view/10.1093/oso/9780198836841.001.0001/oso-9780198836841-chapter-3}{10.1093/oso/9780198836841.003.0003}} \\
3. & \hangindent=5mmMurray-Stoker, K. M., D. P. Batzer, \textbf{D. Murray-Stoker}, and J. V. McHugh. 2020. Shifts in the community composition of caddisflies (Insecta: Trichoptera) in a subtropical river over three decades. \textit{Ecological Entomology} 45: 514-524. DOI: {\href{https://resjournals.onlinelibrary.wiley.com/doi/full/10.1111/een.12822}{10.1111/een.12822}} | {\href{https://doi.org/10.6084/m9.figshare.14237687.v1}{Data \& Code}} \\
2. & \hangindent=5mmMurray, K. M., \textbf{D. Stoker}, C. M. Pringle, and T. N. Simon. 2018. Is spatial variation in population size structures of a stream-dwelling caddisfly due to the altered effects of a predator by a third-party species? \textit{Hydrobiologia} 820: 65-77. DOI: {\href{https://link.springer.com/article/10.1007/s10750-018-3674-0}{10.1007/s10750-018-3674-0}} | {\href{https://doi.org/10.6084/m9.figshare.5856651.v1}{Data \& Code}} \\
1. & \hangindent=5mm\textbf{Stoker, D.}, A. J. Falkner, K. M. Murray, A. K. Lang, T. R. Barnum, J. Hepinstall-Cymerman, M. J. Conroy, R. J. Cooper, and C. M. Pringle. 2017. Decomposition of terrestrial resource subsidies in headwater streams: Does consumer diversity matter? \textit{Ecosphere} 8: e01868. DOI: {\href{https://esajournals.onlinelibrary.wiley.com/doi/full/10.1002/ecs2.1868}{10.1002/ecs2.1868}} | {\href{https://doi.org/10.6084/m9.figshare.6025811.v1}{Data \& Code}} | Undergraduate Senior Thesis \\
\end{longtable}

 \smallskip
 \noindent $^{+}$ Equal contributors
 
 \smallskip
 \noindent $^{*}$ Undergraduate co-author

\bigskip




%%% Manuscripts (In Prep or Under Review/Revision) %%%

%\noindent\Large{Manuscripts (In Prep)} 
%\normalsize
%\bigskip

%\def\arraystretch{1.4}
%\noindent \begin{longtable}{@{} p{0.5cm} >{\raggedright\arraybackslash}p{16.7cm}}
%1. & \hangindent=5mm\textbf{D. Murray-Stoker},  L. Rossi, and M. T. J. Johnson. Diversity %and assembly of the microbiome of a leguminous plant along an urbanization gradient. In prep. \\
 %\end{longtable}


%\bigskip




\newpage
%%% Teaching  %%%

\noindent\Large{\textbf{Teaching}}
\normalsize


\def\arraystretch{1.1}
\begin{longtable}{@{} >{\raggedright\arraybackslash}p{15.5cm} >{\raggedright\arraybackslash}p{1.7cm}}


\textbf{Clayton State University} & \\
\textbf{Lectures} \\
\hspace{10mm} BIOL2251: Anatomy \& Physiology I  & 2024 \\
 
\smallskip
 
\textbf{Labs} \\
\hspace{10mm} BIOL2251L: Anatomy \& Physiology I Lab & 2024 \\

  
\end{longtable}



\def\arraystretch{1.1}
\begin{longtable}{@{} >{\raggedright\arraybackslash}p{15.5cm} >{\raggedright\arraybackslash}p{1.7cm}}


\textbf{University of Toronto} & \\
\textbf{Course Instructor} \\
   \hspace{10mm} BIO205: Ecology (90 students) & 2023 \\
 
 \smallskip
 
 \textbf{Teaching Assistantships} & \\
 \hspace{5mm} \textbf{Teaching Roles} \\
  \hspace{10mm} BIO205: Ecology (24 students/lab) & 2018---2020, 2023 \\
  \hspace{10mm} BIO342: Evolutionary Biology (25 students/lab) & 2023 \\
  \hspace{10mm} BIO360: Biometrics I (48 students/lab)& 2019-2021, 2023 \\

 \hspace{5mm} \textbf{Administrative Roles} \\
  \hspace{10mm} BIO205: Ecology (c. 300 students) & 2021---2022 \\
  \hspace{10mm} BIO153: Diversity of Organisms (c. 900 students) & 2022 \\
  
\end{longtable}
 
\bigskip





%%% Mentoring %%%

\noindent\Large{\textbf{Mentoring}}
\normalsize
\bigskip

\def\arraystretch{1.1}
\noindent \begin{longtable}{@{} >{\raggedright\arraybackslash}p{15.5cm} >{\raggedright\arraybackslash}p{1.7cm}}

\textbf{Fan Peng Kong and Fathima Amanat}, Undergraduate Students, Independent Research & 2020-2022 \\
  \hspace{5mm}Project: \textit{Environmental filtering and habitat (mis)matching of riverine invertebrate metacommunities} &  \\
 
 \smallskip
 
\textbf{Elana Maria}, Undergraduate Student, Research Opportunity Program & 2021 \\
  \hspace{5mm}Project: \textit{Evo-eco feedbacks in a legume-rhizobia mutualism} &  \\

 \end{longtable}
 
 %\bigskip





\newpage
 %%% Pedagogical Development%%%

\noindent\Large{\textbf{Pedagogical Development}}
\normalsize
\bigskip


\def\arraystretch{1.1}
\noindent \begin{longtable}{@{} >{\raggedright\arraybackslash}p{15.5cm} >{\raggedright\arraybackslash}p{1.7cm}}

 \textbf{Advanced University Teaching Preparation Certificate}  & 2021---2023\\
University of Toronto, Teaching Assistant Training Program \\
Workshops (36 hours) & \\
\hspace{2mm} \textbf{Equity \& Access} \\
  \hspace{5mm} Identify, Assist, Refer Plus (IAR+) Training & \\
  \hspace{5mm} Identifying and Addressing Microaggressions in the University Classroom & \\
  \hspace{5mm} Cultural Humility in Teaching & \\
  \hspace{5mm} Re-Envisioning Discomfort in the Classroom & \\
  \hspace{5mm} Contemplative Strategies in an Anti-Oppressive Classroom & \\
  \hspace{5mm} Personalizing Your Land Acknowledgement & \\
  \hspace{5mm} Dialoguing with Indigenous Perspectives on Reconciliation Education & \\
\hspace{2mm} \textbf{Reflective Practice \& Teaching Skills} \\
  \hspace{5mm} Fundamentals of Course and Assessment Design & \\
  \hspace{5mm} Avoiding Crickets: Discussion Strategies and Activities & \\
  \hspace{5mm} Undergraduate Mentorship and Training in the Research Laboratory & \\
  \hspace{5mm} Teaching \& Learning in Uncertainty: The Role of Care and Kindness in the Classroom & \\
  \hspace{5mm} Personal \& Pedagogical Value of Failure & \\
  \hspace{5mm} Building a Learning Community in Your Classroom & \\
\hspace{2mm} \textbf{Educational Technology} \\
  \hspace{5mm} Engaging in Quantitative and Qualitative Data Interpretation & \\
  \hspace{5mm} Online, In-Person, and In Between: Navigating the Changing Educational Landscapes & \\
  \hspace{5mm} Building Community in Online Learning Environments & \\
\hspace{2mm} \textbf{Open Category} \\
  \hspace{5mm} Introduction to Active Learning: Theory \& Strategy & \\
  \hspace{5mm} Grading Strategies for Teaching Assistants & \\

Practicum (6 hours) & \\
\hspace{2mm} \hangindent=5mm Two sessions, each consisting of presenting a 10-minute lesson, listening to and participating in other lessons, and giving and receiving feedback.

\end{longtable}


\def\arraystretch{1.1}
\noindent \begin{longtable}{@{} >{\raggedright\arraybackslash}p{15.5cm} >{\raggedright\arraybackslash}p{1.7cm}}


 \textbf{Teaching in Higher Education Course}  & 2022\\
THE500, Woodsworth College, University of Toronto \\
\hangindent=5mm12-week course focused on the practice of teaching in higher education, with coverage and discussion on topics such as syllabus design, effective learning experiences, universal design for learning, teaching technologies, and accessibility. Included a peer observation and evaluation of teaching practices. & \\
\end{longtable}

\def\arraystretch{1.1}
\noindent \begin{longtable}{@{} >{\raggedright\arraybackslash}p{15.5cm} >{\raggedright\arraybackslash}p{1.7cm}}

 \textbf{Ecological Society of America Short Courses}  & 2021\\
Annual Meeting of the Ecological Society of America & \\
  \hspace{5mm} Incorporating Diversity, Equity, Inclusion, and Social Justice into Ecology Curricula & \\
  \hspace{5mm} Bringing Computational Data Sciences to Undergraduate Ecology Classroom & \\
\end{longtable}

\bigskip





%%% Presentations %%%

\noindent\Large{\textbf{Presentations}} 
\normalsize
\bigskip

\def\arraystretch{1.4}
\noindent \begin{longtable}{@{} >{\raggedright\arraybackslash}p{17.2cm}}
\hangindent=5mmRichter, C., \textbf{D.Murray-Stoker}, and M. den Hollander 2024. Lowering barriers without scaffolds: how to introduce ecology students to hypotheses and R. Annual Meeting of the Ecological Society of America, Long Beach, CA, USA. \textit{(Poster)} \\
\hangindent=5mm\textbf{Murray-Stoker, D.} 2023. Evolutionary ecology of plant-microbe interactions in urban environments. University of Toronto Mississauga Department of Biology Seminar Series, Mississauga, ON, CA. \textit{(Oral)} \\
\hangindent=5mm\textbf{Murray-Stoker, D.}, J. S. Santangelo, M. Szulkin, and M. T. J. Johnson. 2022. Quantifying urban environmental gradients across varying climates on a global scale. Joint Meeting of the Canadian Society for Ecology and Evolution and the Ecological Society of America, Montreal, QC, CA. \textit{(Oral)} \\
\hangindent=5mm\textbf{Murray-Stoker, D.}, and M. T. J. Johnson. 2022. Local adaptation between white clover and rhizobia in the urban mosaic. Annual Meeting of the Society for the Study of Evolution, Cleveland, OH, USA. \textit{(Oral)} \\
\hangindent=5mm Elana Maria$^{*}$, \textbf{D. Murray-Stoker}, and M. T. J. Johnson. 2022. Evo-eco feedbacks in a legume-rhizobia mutualism. Summer Undergraduate Research Fair, Mississauga, ON, CA. \textit{(Poster)} \\
\hangindent=5mm\textbf{Murray-Stoker, D.}, and M. T. J. Johnson. 2021. Ecological consequences of urbanization on a legume-rhizobia mutualism. Annual Meeting of the Ecological Society of America, Virtually Anywhere. \textit{(Oral)} \\
\hangindent=5mm\textbf{Stoker, D.}, A. J. Falkner, K. M. Murray, A. K. Lang, T. R. Barnum, J. Hepinstall-Cymerman, M. J. Conroy, R. J. Cooper, and C. M. Pringle. 2016. Decomposition of terrestrial resource subsidies in headwater streams: Does consumer diversity matter? Odum School of Ecology Graduate Student Symposium, Athens, GA, USA. \textit{(Poster)} \\
\hangindent=5mm\textbf{Stoker, D.}, A. J. Falkner, K. M. Murray, A. K. Lang, T. R. Barnum, J. Hepinstall-Cymerman, M. J. Conroy, R. J. Cooper, and C. M. Pringle. 2015. Decomposition of terrestrial resource subsidies in headwater streams: Does consumer diversity matter? Annual Meeting of the Society for Freshwater Science, Milwaukee, WI, USA. \textit{(Poster)} \\
\hangindent=5mm\textbf{Stoker, D.}, A. J. Falkner, K. M. Murray, A. K. Lang, T. R. Barnum, J. Hepinstall-Cymerman, M. J. Conroy, R. J. Cooper, and C. M. Pringle. 2015. Decomposition of terrestrial resource subsidies in headwater streams: Does consumer diversity matter? Annual Southeastern Ecology and Evolution Conference, Athens, GA, USA. \textit{(Oral)} \\
\hangindent=5mmBarnum, T. R., J. T. Wootton, R. J. Bixby, J. M. Drake, C. Colon-Gaud, \textbf{D. Stoker}, A. T. Rugenski, T. C. Frauendorf, S. J. Connelly, S. S. Kilham, M. R. Whiles, K. R. Lips, and C. M. Pringle. 2014. Examining why grazing mayflies do not functionally compensate for the top-down control of algal communities following disease-driven tadpole declines in a Neotropical stream. Annual Meeting of the Ecological Society of America, Sacramento, CA, USA. \textit{(Oral)}
\end{longtable}

\smallskip

\noindent $^{*}$ Undergraduate mentee presenter

\bigskip



\newpage






%%% Academic Service %%%

\noindent\Large{\textbf{Academic Service}} 
\normalsize
\bigskip

\def\arraystretch{1.1}
\noindent \begin{longtable}{@{} >{\raggedright\arraybackslash}p{15.5cm} >{\raggedright\arraybackslash}p{1.7cm}}

\textbf{Member}, School of Sciences Experiential Learning Committee & 2024---Present \\
\textbf{Member}, School of Sciences New Programs Committee & 2024---Present \\
\textbf{Co-Founder}, U of T EEB Pedagogy Reading Group & 2023---2024 \\
\textbf{Co-Vice President}, UTM Biology Graduate Student Society & 2023---2024 \\
\textbf{Co-President}, UTM Biology Graduate Student Society & 2022---2023 \\
\textbf{Secretary}, UTM Biology Graduate Student Society & 2021---2022 \\
\textbf{Departmental Steward}, Canadian Union of Public Employees 3902 & 2021---2022 \\
\textbf{Member}, UTM Biology Equity, Diversity, \& Inclusion Committee & 2020---2022 \\
\textbf{Member}, U of T EEB Wellness Committee, University of Toronto & 2020---2021 \\
\end{longtable}

\bigskip



%%% Honors & Awards %%%

\noindent\Large{\textbf{Honors \& Awards}}
\normalsize
\bigskip

\noindent \begin{longtable}{@{} >{\raggedright\arraybackslash}p{16cm} >{\raggedright\arraybackslash}p{1.2cm}}
Rustom H. Dastur Graduate Scholarship in Ecology \& Evolutionary Biology & 2018---2023\\ 
University of Toronto Faculty of Arts \& Science Program-Level Fellowship & 2018---2023 \\
Josh Laerm Memorial Outstanding Undergraduate Award & 2015 \\
Zell Miller Scholarship & 2011---2016 \\
\end{longtable}

\bigskip




%%% Funding %%%

\noindent\Large{\textbf{Funding}}
\normalsize
\bigskip

\noindent \begin{longtable}{@{} >{\raggedright\arraybackslash}p{16cm} >{\raggedleft\arraybackslash}p{1.2cm}}
University of Toronto Doctoral Completion Award (4000 CAD) & 2023 \\
University of Toronto Ecology \& Evolutionary Biology Research Grant (2000 CAD) & 2021 \\ 
American Society of Naturalists Student Research Award (2000 USD) & 2021 \\
Centre for Urban Environments Research Fund (2000 CAD) & 2021 \\
CURO Undergraduate Research Assistantship (2000 USD) & 2015 \\
Society for Freshwater Science Undergraduate Travel Award (600 USD) & 2015 \\
Thelma Richardson \& Frank Golley Undergraduate Support Award (500 USD) & 2013 \\
\end{longtable}

\bigskip



%%% Professional Engagement %%%

\noindent\Large{\textbf{Professional Engagement}} 
\normalsize
\bigskip

\noindent{\textbf{Peer Reviews:}  Ecology (1), Ecology \& Evolution (1), Ecology Letters (2), Ecosphere (2), Hydrobiologia (2), Journal of Animal Ecology (7), Journal of Urban Ecology (2), Oecologia (2), Oikos (2), Peer Community in Ecology (6), Peer Community in Evolutionary Biology (2), Proceedings of the Royal Society B: Biological Sciences (3), Scientific Reports (1), Soil Biology \& Biochemistry (2)}


\bigskip

\noindent{\textbf{Member:} Society for the Study of Evolution, Ecological Society of America, Society for the Advancement of Biology Education Research, Human Anatomy and Physiology Society, Sigma Xi}

\bigskip





\end{document}